RNA-seq Analysis

### 2021-04-14 inst/analysis/rnaseq.Rmd
work on TF binding analysis

```{r}
withr::with_dir(here::here(), {
  rnaseq_pca <- tar_read(rnaseq_pca)
  rnaseq_different_differences <- tar_read(rnaseq_different_differences)
})
```

@@

```{r}
head(rnaseq_different_differences, 20)
```

>>>>

```{r}
withr::with_dir(here::here(), {
  rnaseq_pca <- tar_read(rnaseq_pca)
  rnaseq_different_differences <- tar_read(rnaseq_different_differences)
  rnaseq_gsea_plot <- tar_read(rnaseq_gsea_plot)
})
```

@@

```{r}
head(rnaseq_different_differences, 20) %>% 
  my_kable()
```

## Gene Set Enrichment Analysis

```{r}
rnaseq_gsea_plot
```

## Transcription Factor Analysis

```{r}

```

```{r}

```

```{r}
tf_rnk$TFranking_plot
```
